---
title: "ESM204_a2"
author: "Richard Viebrock"
date: "4/19/2020"
output:
  pdf_document: default
  word_document: default
---

```{r setup, include=FALSE, ncols = 2}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
```

```{r}

# Attach necessary packaegs

library(tidyverse)
library(ggplot2)
library(wesanderson)
library(janitor)
library(broom)
library(nlstools)

```

```{r}

# Read in data

raw_data <- read_csv("HW2_Data.csv") %>% 
  clean_names()

```

```{r}
# Create function to estimate abatement costs

a_lm <- lm(mc_a ~ abatement, data = raw_data)
b_lm <- lm(mc_b ~ abatement, data = raw_data)
c_lm <- lm(mc_c ~ abatement, data = raw_data)
d_lm <- lm(mc_d ~ abatement, data = raw_data)
summary(d_lm)

```

```{r}
# Naming Things
a_y <- a_lm$coefficients[1]
a_1 <- a_lm$coefficients[2]
b_y <- b_lm$coefficients[1]
b_1 <- b_lm$coefficients[2]
c_y <- c_lm$coefficients[1]
c_1 <- c_lm$coefficients[2]
d_y <- d_lm$coefficients[1]
d_1 <- d_lm$coefficients[2]
```

```{r}
# Create functions using lm outputs

# Abatement Functions
a_eq <- function(x) {y = a_y + a_1*x}
b_eq <- function(x) {y = b_y + b_1*x}
c_eq <- function(x) {y = c_y + c_1*x}
d_eq <- function(x) {y = d_y + d_1*x}
z <- 0:150

# Pollution Demand Functions p(q)
a_price <- function(q) {y = a_y + a_1*(170-q)}
b_price <- function(q) {y = b_y + b_1*(200-q)}
c_price <- function(q) {y = c_y + c_1*(230-q)}
d_price <- function(q) {y = d_y + d_1*(300-q)}
agg_price <- function(q) {p = (a_y + a_1*(170-q)) + (b_y + b_1*(200-q)) + (c_y + c_1*(230-q))}
za <- 0:250

# Pollution Demand Functions q(p)
a_quant <- function(p) {q = 170 - ((p-a_y)/a_1)}
b_quant <- function(p) {q = 200 - ((p-b_y)/b_1)}
c_quant <- function(p) {q = 230 - ((p-c_y)/c_1)}
d_quant <- function(p) {q = 300 - ((p-d_y)/d_1)}
agg_quant <- function(p) {q =  600 - ((p-a_y)/a_1) - ((p-b_y)/b_1) - ((p-c_y)/c_1)}
agg_quant_all <- function(p) {q =  900 - ((p-a_y)/a_1) - ((p-b_y)/b_1) - ((p-c_y)/c_1) - ((p-d_y)/d_1)}

```

3. Analysis of Country X Policies
a. Cap on Carbon
  - (1) Total cost of meeting the target in country X
  - (2) The cost (or benefit) to each sector
  - (3) The tax revenue generated from policy

```{r}

# Question 3a - Cap on Carbon (Use 1/2 B*H)
# Use abatement equations to calculate the total cost of abatement up to the 100th unit

# Calculate price of abatement at 100th unit (this is the triangle height)
abat_price_a <- a_eq(100)
abat_price_b <- b_eq(100)
abat_price_c <- c_eq(100)

# C does not cross y-axis in positive quadrant. Identify where C crosses x axis to determine triangle length
abat_c_quant <- function(p) {q = (p-c_y)/c_1}
abat_quant_c <- abat_c_quant(0)
abat_price_c_a <- c_eq(0)
under_curve_c <- (0.5)*(abat_price_c_a)*26.8

# Ansers for Q3 part a
cost_a <- (0.5)*(100)*(abat_price_a-a_y) + (a_y*100)
cost_b <- (0.5)*(100)*(abat_price_b-b_y) + (b_y*100)
cost_c <- (0.5)*(100-abat_quant_c)*(abat_price_c) + under_curve_c
cost_total <- sum(cost_a, cost_b, cost_c)
tax_revenue_cap <- 0

integrate()

```

b. Tax on Carbon
  - (1) Total cost of meeting the target in country X
  - (2) The cost (or benefit) to each sector
  - (3) The tax revenue generated from policy

```{r}

# Carbon tax - at what price is Q of pollution = 300?
# Use aggregate demand function (in excel) to determine price at 600 and 300 units (one day, learn how to do this in R)

# Values correlating with emissions quantities (*values derived using Excel SOlver)
# price_600 <- 0.361002895751039
price_300 <- 56.0540158661948
tax_price <- price_300
# Maybe  (- price_600)

# Hey there, forker. It's nice to see you. Thanks for forking this repo. 

# Calculate units produced at tax price
tax_quant_a <- a_quant(tax_price)
tax_quant_b <- b_quant(tax_price)
tax_quant_c <- c_quant(tax_price)

# Two options - (1) calculate required abatement and then determine cost of abatement OR (2) calculate the cost of the tax on each sector by multiplying new quantity of units produced by tax cost. 

# Answers - Option #2
tax_cost_a <- (tax_quant_a*tax_price) + (0.5)*(tax_price)*(a_quant(0) - tax_quant_a)
tax_cost_b <- (tax_quant_b*tax_price) + (0.5)*(tax_price)*(b_quant(0) - tax_quant_b)
tax_cost_c <- (tax_quant_c*tax_price) + (0.5)*(tax_price)*(c_quant(0) - tax_quant_c)
tax_cost_tax <- sum(tax_cost_a, tax_cost_b, tax_cost_c)

test_01 <- a_quant(0)
test_02 <- b_quant(0)
test_03 <- c_quant(0)

# Tax revenue
tax_rev_a <- tax_quant_a*tax_price
tax_rev_b <- tax_quant_b*tax_price
tax_rev_c <- tax_quant_c*tax_price
tax_revenue_tax <- sum(tax_rev_a, tax_rev_b, tax_rev_c)

ggplot()+
  stat_function(aes(za, color = "Sector A"), fun = a_price, size = 1, show.legend = TRUE)+
  stat_function(aes(za, color = "Sector B"), fun = b_price, size = 1, show.legend = TRUE)+
  stat_function(aes(za, color = "Sector C"), fun = c_price, size = 1, show.legend = TRUE)+
  geom_hline(aes(yintercept = 56.05), color = "purple", size = 1)+
  # stat_function(aes(za, color = "Sector D"), fun = d_price, size = 1, show.legend = TRUE)+
  # stat_function(aes(za, coord_flip = TRUE), color = "black", fun = agg_price, size = 1, show.legend = FALSE)+
  scale_y_continuous(limits = c(0, 300),
                     expand = c(0, 0))+
  scale_x_continuous(limits = c(0, 300),
                     expand = c(0, 0))+
  scale_color_manual(values = c("darkred", "darkblue", "darkorange", "darkgreen"))+
  labs(x = "Pollution (Metric Tons)",
       y = "Price (USD / Metric Ton)",
       title = "Figure 2: Demand for Pollution",
       color = "Sector")+
  theme_classic()+
  theme(legend.position = c(0.95, 0.95),
        legend.justification = c("right", "top"),
        legend.background = element_rect(fill = "gray85"))

```

c. Cap & Trade
  - (1) Total cost of meeting the target in country X
  - (2) The cost (or benefit) to each sector
  - (3) The tax revenue generated from policy

```{r}

# Units produced per sector found at price where agg demand curve = 300 units. See "price_300" above. 
# optimal units same as tax_quant for each sector. Cost comes in form of abatement, however, not tax cost. 

# Calculate units produced at optimal quantity
ct_quant_a <- tax_quant_a
ct_quant_b <- tax_quant_b
ct_quant_c <- tax_quant_c

# Calculate required reductions due to cap
cap_abat_a <- 170 - 100
cap_abat_b <- 200 - 100
cap_abat_c <- 230 - 100

# Calculate required abatement to achieve these units produced
ct_abat_a <- 170 - ct_quant_a
ct_abat_b <- 200 - ct_quant_b
ct_abat_c <- 230 - ct_quant_c

# Result of trade
ct_trade_a <- cap_abat_a - ct_abat_a
ct_trade_b <- cap_abat_b - ct_abat_b
ct_trade_c <- cap_abat_c - ct_abat_c

# Calculate cost of abatement at nth unit - costs would be split more equitably than this because of trading. do that ish later. 
ct_cost_a <- (0.5)*(ct_abat_a)*(abat_price_a-a_y) + (a_y*ct_abat_a)
ct_cost_b <- (0.5)*(ct_abat_b)*(abat_price_b-b_y) + (b_y*ct_abat_b)
ct_cost_c <- (0.5)*(ct_abat_c-abat_quant_c)*(abat_price_c)+ under_curve_c
ct_cost_total <- sum(ct_cost_a, ct_cost_b, ct_cost_c) 

# Net result of trade
ct_net_a <- ct_cost_a + ct_trade_a*price_300
ct_net_b <- ct_cost_b + ct_trade_b*price_300
ct_net_c <- ct_cost_c + ct_trade_c*price_300
ct_net_total <- sum(ct_net_a, ct_net_b, ct_net_c)

```

Question 4 - To country Y, or not to country Y, that is the question

```{r, out.width = c('50%', '50%'), fig.show = 'hold'}

test <- a_price(106)

# Use aggregate demand (all sectors) function to determine price at 900 and 600 units (300 country x +300 country y)
price_600_y <- 38.9080483484851

# Optimal production quantities with merged market (countries x & y)
y_quant_a <- a_quant(price_600_y)
y_quant_b <- b_quant(price_600_y)
y_quant_c <- c_quant(price_600_y)
y_quant_d <- d_quant(price_600_y)

# Calculate required abatement amounts by sector 
y_abat_a <- 170 - y_quant_a
y_abat_b <- 200 - y_quant_b
y_abat_c <- 230 - y_quant_c
y_abat_d <- 300 - y_quant_d

# Calculate results of trade
y_trade_a <- cap_abat_a - y_quant_a
y_trade_b <- cap_abat_b - y_quant_b
y_trade_c <- cap_abat_c - y_quant_c 
y_trade_d <- 300 - y_quant_d 

# Figuring shit out at the last minute
d_eq_69 <- function(p) {(q = p-d_y)/d_1}
abat_quant_d <- d_eq_69(0)
stupid_shit <- d_eq(0)
  

#Calculate required abatement costs by sector
y_cost_a <- (0.5)*(y_abat_a)*(price_600_y-a_y) + (a_y*y_abat_a)
y_cost_b <- (0.5)*(y_abat_b)*(price_600_y-b_y) + (b_y*y_abat_b)
y_cost_c <- (0.5)*(y_abat_c-abat_quant_c)*(price_600_y) + under_curve_c
y_cost_d <- (0.5)*(y_abat_d-abat_quant_d)*(price_600_y) + (0.5)*(stupid_shit)*abat_quant_d
y_cost_total <- sum(y_cost_a, y_cost_b, y_cost_c, y_cost_d)

# Calculate net cost post trading
y_net_a <- y_cost_a + y_trade_a*price_600_y
y_net_b <- y_cost_b + y_trade_b*price_600_y
y_net_c <- y_cost_c + y_trade_c*price_600_y
y_net_d <- y_cost_d + y_trade_d*price_600_y
y_net_cost <- sum(y_net_a, y_net_b, y_net_c, y_net_d)
```

```{r, out.width = c("50%", "50%"), fig.show = "hold"}

# Plots for appendix

# Plot marginal abatement 
ggplot() +
  stat_function(aes(z, color = "Sector A"), fun = a_eq, size = 1, show.legend = TRUE)+
  stat_function(aes(z, color = "Sector B"), fun = b_eq, size = 1, show.legend = TRUE)+
  stat_function(aes(z, color = "Sector C"), fun = c_eq, size = 1, show.legend = TRUE)+
  # stat_function(aes(z, color = "Sector D"), fun = d_eq, size = 1, show.legend = TRUE)+
  scale_y_continuous(limits = c(0, 200),
                     expand = c(0, 0))+
  scale_x_continuous(limits = c(0, 200),
                     expand = c(0, 0))+
  scale_color_manual(values = c("darkred", "darkblue", "darkorange", "darkgreen"))+
  labs(x = "Abatement (Metric Tons)", 
       y = "Price (USD / Metric Ton)",
       title = "Figure 1: Marginal Abatement Cost",
       color = "Sector")+
  theme_classic()+
  theme(legend.position = c(0.20, 0.95),
        legend.justification = c("right", "top"),
        legend.background = element_rect(fill = "gray85"))

# Plot demand for pollution
ggplot()+
  stat_function(aes(za, color = "Sector A"), fun = a_price, size = 1, show.legend = TRUE)+
  stat_function(aes(za, color = "Sector B"), fun = b_price, size = 1, show.legend = TRUE)+
  stat_function(aes(za, color = "Sector C"), fun = c_price, size = 1, show.legend = TRUE)+
  geom_hline(aes(yintercept = 56.05), color = "purple", size = 1)+
  stat_function(aes(za, color = "Sector D"), fun = d_price, size = 1, show.legend = TRUE)+
  # stat_function(aes(za, coord_flip = TRUE), color = "black", fun = agg_price, size = 1, show.legend = FALSE)+
  scale_y_continuous(limits = c(0, 300),
                     expand = c(0, 0))+
  scale_x_continuous(limits = c(0, 300),
                     expand = c(0, 0))+
  scale_color_manual(values = c("darkred", "darkblue", "darkorange", "darkgreen"))+
  labs(x = "Pollution (Metric Tons)",
       y = "Price (USD / Metric Ton)",
       title = "Figure 2: Demand for Pollution",
       color = "Sector")+
  theme_classic()+
  theme(legend.position = c(0.95, 0.95),
        legend.justification = c("right", "top"),
        legend.background = element_rect(fill = "gray85"))


```

```{r}
# Appendix - Regression Analysis

raw_data_02 <- raw_data %>%
  pivot_longer("mc_a":"mc_d",
  names_to = "sector",
  values_to = "mc")

# Plot estimated marginal abatement costs

ggplot(data = raw_data_02, aes(x = abatement, y = mc))+
  geom_line()+
  geom_point()+
  geom_smooth(method = "lm",
              se = TRUE)+
  facet_wrap(~sector,
              scale = "free")+
  labs(y = "marginal cost")

```


```{r}

# Hello there, beautiful code that no longer is relevant

# ggplot()+
#   stat_function(aes(za), color = "darkred", fun = a_demand, size = 1, show.legend = FALSE)+
#   stat_function(aes(za), color = "darkblue", fun = b_demand, size = 1, show.legend = FALSE)+
#   stat_function(aes(za), color = "darkorange", fun = c_demand, size = 1, show.legend = FALSE)+
#   # stat_function(aes(za), color = "darkgreen", fun = d_demand, size = 1, show.legend = FALSE)+
#   # stat_function(aes(za, coord_flip = TRUE), color = "black", fun = agg_quant, size = 1, show.legend = FALSE)+
#   scale_y_continuous(limits = c(0, 300),
#                      expand = c(0, 0))+
#   scale_x_continuous(limits = c(0, 250),
#                      expand = c(0, 0))+
#   labs(x = "Pollution (Metric Tons)",
#        y = "Price (USD / Metric Ton)",
#        title = "Demand for Pollution")+
#   theme_classic()
# 
# ggplot()+
#   stat_function(aes(za), color = "darkred", fun = a_quant, size = 1, show.legend = FALSE)+
#   stat_function(aes(za), color = "darkblue", fun = b_quant, size = 1, show.legend = FALSE)+
#   stat_function(aes(za), color = "darkorange", fun = c_quant, size = 1, show.legend = FALSE)+
#   # stat_function(aes(za), color = "darkgreen", fun = d_demand, size = 1, show.legend = FALSE)+
#   # stat_function(aes(za, coord_flip = TRUE), color = "black", fun = agg_quant, size = 1, show.legend = FALSE)+
#   scale_y_continuous(limits = c(0, 300),
#                      expand = c(0, 0))+
#   scale_x_continuous(limits = c(0, 250),
#                      expand = c(0, 0))+
#   labs(x = "Pollution (Metric Tons)",
#        y = "Price (USD / Metric Ton)",
#        title = "Demand for Pollution")+
#   theme_classic()

# Regression Analysis

# b_lm_02 <- lm(mc_b ~ poly(abatement, 2, raw = TRUE), data = raw_data)
# b_nls <- nls(mc_b ~ K/(1 + A*exp(-r*abatement)), data = raw_data, 
# start = list(K = 60, A = 50, r = 0.39), trace = TRUE)
# b_lm <- lm(mc_b ~ poly(abatement, 2, raw = TRUE), data = raw_data)
# c_lm <- lm(mc_c ~ poly(abatement, 2, raw = TRUE), data = raw_data)
# d_lm <- lm(mc_d ~ poly(abatement, 2, raw = TRUE), data = raw_data)


# Marginal cost equations

# x_demand <- function(q) {y = 600 - ((q-a_y)/a_1) - ((q-b_y)/b_1) - ((q-c_y)/c_1)}
# b_eq_huh <- function(x) {y = (58.18640)/(1+10.56466*exp(-0.04849*x))}
# b_eq_quad <- function(x) {y = -2.008211 + 0.854358*(x) + -0.003084*(x)^2}
# c_eq <- function(x) {y = 0.321580*(x) + 0.005390*(x^2) - 7.941422}
# d_eq <- function(x) {y = 2.098529 - 0.059765*x + 0.004088*x^2}
# c_eq <- function(x) {y = 1.563e-02*x^2 -2.735e-01*x - 4.553e-05*x^3 - 1.726e+00}
# a_eq_demand <- function(q) {y = 1.663 + 0.513*(170) - 0.513*(q)}
# b_eq_demand <- function(q) {y = y = 8.78529 + 0.39178*(200) - 0.39178*(q)}
# b_eq_demand <- function(q) {y = 8.7853 + 0.3918*(200) - 0.3918*(q)}
# c_eq_demand <- function(q) {y = 0.321580*(230 - q) + 0.005390*(230 - q)*(230 - q) - 7.941422}
# d_eq_demand <- function(q) {y = 2.098529 - 0.059765*(300 - q) + 0.004088*(300 - q)^2}
# a_demand_01 <- function(q) {y = 170 - ((q-a_y)/a_1)}

# # Plot the OG data
# 
# # Modify data frame for graph
# 


```

